An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-25 neurips-19/poly-embed.tex

>>>>

%Bo new
\begin{lemma} \label{lemma:exposed-shortest}
  Let $U$ be a convex, closed set and $u \not\in U$.
  Let $\|\cdot\|$ be a norm.
  Then $\inf_{u^* \in U} \|u-u^*\|$ is achieved by some $u^* \in U$.
  Furthermore, $u^*$ is the unique member of $U$ such that $u = u^* + \alpha v$ for some $\alpha > 0$ and $v$ that exposes $u^*$.
\end{lemma} % Bo new lemma
\begin{proof} % Bo new proof
  \bo{Show $u^*$ is a minimizer if and only if $u = u^* + \alpha v$ for some $\alpha > 0$ where $v$ exposes $u^*$.
  Should be able to cite most or all of this.}
\end{proof} % Bo new proof
%end Bo new
